### 2022-11-24 dissertation/chapters/01-introduction.tex
✨ (chapter4): Review Done
✨ (final-review): Done up till chapter 1

\begin{quotation}
      \noindent ``It is better to solve one problem five different ways, than to solve five problems one way.''
\end{quotation}
\begin{flushright}
      George Polya
\end{flushright}

\noindent
\Acf{ML} is one of the most popular fields of research in \acf{AI} studies today. In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:san-hun:2016}.

@@

\Acfp{FFNN} are specific types of \acp{ANN}~\cite{ref:reed:1999}. A popular field of focus for studying \acp{ANN} is the process by which these models are trained.  The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data. Training of \acp{ANN} is seen as an optimisation problem. The \acs{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic}~\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \acs{ANN}, such that a specified objective function is minimised. The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.

@@

The following section outlines the research problem that this dissertation aims to address and is followed by a motivation for this research.

@@

Many different heuristics have been developed and used to train \acp{FFNN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train the \acs{FFNN} is required in order to yield optimal results. This process is often non-trivial and could be a time-consuming exercise.  Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem dependent~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.

@@

\acp{FFNN} training is seen as a computational search problem. \acf{HH} as defined by Burke et al.~\cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''. \acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.

\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.~\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics). \acp{HH} relieve the burden of having to select the best heuristic to use by trial and error. Furthermore, \acp{HH} can generally be applied to multiple problems given that the set of low-level heuristics include heuristics that have the potential to solve the problem at hand~\cite{ref:burke:2010}. Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of \acp{FFNN} training.

@@

      \item Provide a statistically sound analysis of the results obtained from the empirical study.
\end{itemize}

\noindent
By achieving the objectives outlined above, a number of research contributions are made. These contributions are presented in this following section.

@@

      \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems. It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics (for the particular problem) included in the heuristic selection pool.

@@

      \item \textbf{Chapter~\ref{chap:results}} provides and discusses the results of the empirical study in detail. A baseline comparison is done by comparing the performance of the \Acs{BHH} to that of all the individual lower-level heuristics on all datasets. These datasets include classification and regression problems of various sizes and complexity.  Detailed results are presented on the performance of the \Acs{BHH} as a selection mechanism for \acp{HH} and a brief comparison is made to other selection mechanisms. Finally, results are presented on the effects of the hyper-parameters of the \Acs{BHH} on the training process. Discussions follow on how the \Acs{BHH} is shown to automate the selection of the best heuristic during the training of \acp{FFNN}, as applied to a range of problems, alleviating the burden on researchers to apply traditional trial and error approaches. The chapter is concluded with a brief argument in favor of the general applicability of the \Acs{BHH} to more problem domains.

@@

\noindent
This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:

\begin{itemize}
      \item \textbf{Appendix~\ref{app:backpropagation}} provides a full breakdown of the \acf{BP} algorithm as presented by~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007}.

      \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.

@@

\noindent
To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.

>>>>

\begin{quotation}
      \noindent ``It is better to solve one problem five different ways, than to solve five problems one way.''
\end{quotation}
\begin{flushright}
      - George Polya
\end{flushright}

\Acf{ML} is one of the most popular fields of research in \acf{AI} studies today. In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:san-hun:2016}.

@@

\Acfp{FFNN} are specific types of \acp{ANN}~\cite{ref:reed:1999}. A popular field of focus for studying \acp{ANN} is the process by which these models are trained.  The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input data and comparing the produced output data to that of predefined target data. Training of \acp{ANN} is seen as an optimisation problem. The \acs{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic}~\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \acs{ANN}, such that a specified objective function is minimised. The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.

@@

@@

Many different heuristics have been developed and used to train \acp{FFNN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train the \acs{FFNN} is required in order to yield optimal results. This process is often non-trivial and could be a time-consuming exercise.  Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.

@@

Training of \acp{FFNN} is seen as a computational search problem. A \acf{HH}, as defined by Burke et al.~\cite{ref:burke:2010}, is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''. \acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.

\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.~\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics). \acp{HH} relieve the burden of having to select the best heuristic to use by trial and error. Furthermore, \acp{HH} can generally be applied to multiple problems given that the set of low-level heuristics include heuristics that have the potential to solve the problem at hand~\cite{ref:burke:2010}. Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of training \acp{FFNN}.

@@

      \item Provide a statistical analysis of the results obtained from the empirical study.
\end{itemize}

@@

      \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems. It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.

@@

      \item \textbf{Chapter~\ref{chap:results}} provides and discusses the results of the empirical study in detail. A baseline comparison is done by comparing the performance of the \Acs{BHH} to that of all the individual lower-level heuristics on all datasets. These datasets include classification and regression problems of various sizes and complexity.  Detailed results are presented on the performance of the \Acs{BHH} as a selection mechanism for \acp{HH} and a brief comparison is made to other selection mechanisms. Finally, results are presented on the effects of the hyper-parameters of the \Acs{BHH} on the training process. Discussions follow on how the \Acs{BHH} is shown to automate the selection of the best heuristic during the training of \acp{FFNN}, as applied to a range of problems, alleviating the burden on researchers to apply traditional trial and error approaches.

@@

This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:

\begin{itemize}
      \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.

@@

To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.

### 2022-11-24 dissertation/preamble/abstract.tex
✨ (final-review): Done up till chapter 1

    \Large
    \textbf{Abstract}
\end{center}
\noindent
Many different heuristics have been developed and used to train \acfp{FFNN}.  However, selection of the best heuristic to train
\acsp{FFNN} is a time consuming and non-trivial exercise. Careful, systematic
selection is thus required to ensure that the best heuristic is used to train the \acsp{FFNN}. In the past, selection
was done by trial and error. A modern approach is to automate the heuristic selection
process. Often it is found that a single approach is not sufficient. Research has
proposed the use of hybridisation of heuristics. One such approach is referred to
as \acfp{HH}. \acsp{HH} focus on dynamically finding the best heuristic or combinations of heuristics in
heuristic-space by making use of heuristic performance information during training time. One such
implementation of a \acs{HH} is a population-based approach that guides the search process by
dynamically selecting heuristics from a heuristic-pool to be applied to
different entities that represent candidate solutions to the problem-space and
work together to find good solutions. This dissertation introduces a novel population-based \Acf{BHH}. An empirical study is done by
using the \acs{BHH} to train \acsp{FFNN}. An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics each with different search
behaviours. The chosen heuristic pool consists out of classic gradient-based heuristics as well as meta-heuristics. The empirical process was executed on fifteen datasets consisting of classification and regression problems
with varying characteristics. Results are analysed for statistical significance and the \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.\\*[1cm]
\noindent
\parbox{\textwidth}{
    \textbf{Keywords:} hyper-heuristics, meta-learning, feedforward neural
    networks, supervised learning, Bayesian statistics
}
\vfill
\newpage

>>>>

    \Large
    \textbf{Abstract}
\end{center}
\noindent
Many different heuristics have been developed and used to train \acfp{FFNN}.  However, selection of the best heuristic to train \acp{FFNN} is a time consuming and non-trivial exercise. Careful, systematic selection is required to ensure that the best heuristic is used to train \acp{FFNN}. In the past, selection was done by trial and error. A modern approach is to automate the heuristic selection process. Often it is found that a single approach is not sufficient. Research has proposed the use of hybridisation of heuristics. One such approach is referred to as \acfp{HH}. \acsp{HH} focus on dynamically finding the best heuristic or combinations of heuristics in heuristic-space by making use of heuristic performance information. One such implementation of a \acs{HH} is a population-based approach that guides the search process by dynamically selecting heuristics from a heuristic-pool to be applied to different entities that represent candidate solutions to the problem-space, and work together to find good solutions. This dissertation introduces a novel population-based \Acf{BHH}. An empirical study is done by using the \acs{BHH} to train \acsp{FFNN}. An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics each with different search behaviours. The chosen heuristic pool consists out of classic gradient-based heuristics as well as meta-heuristics. The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics. Results are analysed for statistical significance and the \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.\\*[1cm]
\noindent
\parbox{\textwidth}{
    \textbf{Keywords:} hyper-heuristics, meta-learning, feedforward neural networks, supervised learning, Bayesian statistics
}
\vfill
\newpage
